Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Muck around with the example

            \begin{scope}[xshift=2cm, yshift=-3cm, color=black]
            \node at (0, -0.5) {$T$};
            \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
            \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
            \node [fill, circle, inner sep=1.5pt] (c) at (1,2) {};
            \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
            \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
            \node [fill, circle, inner sep=1.5pt] (f) at (1,0) {};
            \node [fill, circle, inner sep=1.5pt] (g) at (2,0) {};
            \node [fill, circle, inner sep=1.5pt] (h) at (2,2) {};

@@

        \end{tikzpicture}
        \caption{Notice that $P$ would be isormorphic to a subgraph of $T$ if the middle vertex in the diamond is removed.}
        \label{fig:subgraphexample}
    \end{center}
\end{figure}
\subsection{Definitions and Notations}

>>>>

            \begin{scope}[xshift=3cm, yshift=-3cm, color=black]
            \node at (0, -0.5) {$T$};
            \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
            \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
            \node [fill, circle, inner sep=1.5pt] (c) at (1,2) {};
            \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
            \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
            \node [fill, circle, inner sep=1.5pt] (f) at (1,0) {};
            \node [fill, circle, inner sep=1.5pt] (g) at (2,0) {};
            \node [fill, circle, inner sep=1.5pt] (h) at (2,2) {};

@@

        \end{tikzpicture}
        \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
        the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
        \label{fig:subgraphexample}
    \end{center}
\end{figure}
\subsection{Definitions and Notations}
